### 2017-08-31 Rmd/c2-landcover-preprocess-2.Rmd
Gigantic first commit of croplandbias repo after being cloned and renamed from SAcropland. Significant changes: 1. Rerrangement of data structure structure--key intermediate inputs/outputs will be kept in inst/extdata/subfolder to install as R library; some other smaller ones are in data/ 2. Paper and figures are in inst/paper 3. Code has been re-run from c1-c9 (yield-production). Numbering of code chapters has been changed because landcover dataset download steps were placed first in standalone chapter (c1-landcover-fetch) 4. Analysis chapters are now stored as vignettes. Rmd folder is staged

## Analyses
### Set-up
```{r, eval = FALSE}
library(SAcropland)
library(gdalUtils)
library(RCurl)
library(RPostgreSQL)
library(rgdal)
library(rgeos)
library(raster)
library(lmisc)
```

Paths
```{r, eval = FALSE}
#setwd("/u/lestes/analyses/SAcropland/")
p_root <- proj_root("SAcropland")
p_fig <- fp(p_root, "SAcropland/external/figures/")
p_data <- fp(p_root, "SAcropland/external/ext_data/")
```

Background data, projections, database connections, and SA grid
```{r, eval = FALSE}
# Get SA shape
if(!file.exists(fp(p_data, "MZshapes.Rdata"))) {
  system("wget http://dl.dropboxusercontent.com/u/31890709/MZshapes.Rdata")
}
load(fp(p_data, "MZshapes.Rdata"))
sa_buf <- gBuffer(sa.shp, width = 3000)

# Connection
drv <- dbDriver("PostgreSQL")
con <- dbConnect(drv, dbname = "SouthAfricaSandbox", user = "postgis", 
                 password = "P0stG1S")

# projections, etc
prjsrid <- 97490  # Albers
prj_sql <- paste0("select proj4text from spatial_ref_sys where srid=", prjsrid)
prjstr <- dbGetQuery(con, prj_sql)$proj4text
gcsid <- 4326  # GCS
gcs_sql <- paste0("select proj4text from spatial_ref_sys where srid=", gcsid)
gcsstr <- dbGetQuery(con, gcs_sql)$proj4text

@@

# Create 1 km grid from sa1kilo to rectify grids against that 
if(!file.exists(fp(p_data, "sagrid.tif"))) {  # already made? 
  sql <- paste("SELECT gid, id, ST_AsText(ST_Centroid(geom)) as center", 
               "FROM sa1kilo")
  geom.tab <- dbGetQuery(con, sql)
  coord.mat <- do.call(rbind, lapply(1:nrow(geom.tab), function(y) {
    strip <- gsub("POINT|\\(|\\)", "", geom.tab[y, 3])
    coord.mat <- do.call(rbind, strsplit(strsplit(strip, ",")[[1]], " "))
  }))
  class(coord.mat) <- "numeric"
  point.tab <- cbind(geom.tab[, 1:2], coord.mat)
  colnames(point.tab)[3:4] <- c("x", "y") 
  pointsXYZ <- point.tab[, c(3:4, 2)]
  sa_r <- rasterFromXYZ(pointsXYZ)
  projection(sa_r) <- sa_buf@proj4string
  sa_r <- writeRaster(sa_r, filename = fp(p_data, "sagrid.tif"), 
                      overwrite = TRUE)
} else {
  sa_r <- raster(fp(p_data, "sagrid.tif"))
}
```

### Bring in landcover datasets
Let's start with the improved/fusion datasets, GLC share and geo-wiki's
```{r, eval = FALSE}
if(!file.exists(fp(p_data, "glcsa_masked.tif"))) {  # see if file exists,  
  # to avoid redoing step
  path <- "/u/lestes/spatial_data/glc_share/"
  url <- "http://www.fao.org/geonetwork/srv/en/resources.get?id=47948&fname=GlcShare_v10_02.zip&acces=private"
  download.file(url, method = "auto", destfile = "glc_share.zip")
  unzip("glc_share.zip", exdir = "glc_share")
  glc <- raster(fp(path, "glc_shv10_02.Tif"))
  projection(glc) <- gcsstr
  glcSA <- crop(glc, y=sa_buf_gcs, file = fp(path, "glcSA.tif"), 
                overwrite = TRUE)  # crop to SA
  gdalwarp(srcfile = glcSA@file@name, 
           dstfile = fp(path, "glcSA_alb.tif"), t_srs = prjstr, 
           tr = c(1000, 1000), r = "bilinear")
  glcSA_alb <- raster(fp(path, "glcSA_alb.tif"))

  # Warp to SA grid
  glcsa <- resample(glcSA_alb, sa_r, method = "bilinear", 
                    filename = fp(path, "glcSA_alb_rect.tif"))
  glcsa_m <- mask(glcsa, sa_r, file = fp(p_data, "glcsa_masked.tif"),
                  overwrite = TRUE)
} else {
  glcsa_m <- raster(fp(p_data, "glcsa_masked.tif"))
}

if(!file.exists(fp(p_data, "geowikisa_masked.tif"))) {  # see if file exists, to avoid redoing step 
   # first downloaded manually from password protected geo-wiki site
  path <- "/u/lestes/spatial_data/geowiki/"
  unzip("cropland_hybrid_14052014v8.zip", exdir= "geowiki") 
  geowiki <- raster(fp(path, "Hybrid_14052014V8.img"))
  projection(geowiki) <- gcsstr
  geowikiSA <- crop(geowiki, y=sa_buf_gcs, 
                    file = fp(path, "geowikiSA.tif"))  # crop to SA
  gdalwarp(srcfile = geowikiSA@file@name, 
           dstfile = fp(path, "geowikiSA_alb.tif"), t_srs = prjstr, 
           tr = c(1000, 1000), r = "bilinear")
  geowikisa_alb <- raster(fp(path, "geowikiSA_alb.tif"))
  geowikisa <- resample(geowikisa_alb, sa_r, method = "bilinear", # Warp to SA
                        filename = fp(path, "geowikisa_alb_rect.tif"))    
  geowikisa_m <- mask(glcsa, sa_r, 
                      file = fp(p_data, "geowikisa_masked.tif"), 
                      overwrite = TRUE)
} else {
  geowikisa_m <- raster(fp(p_data, "geowikisa_masked.tif"))
}
```

And the standard products, Globcover 2009 and MODIS
```{r, eval = FALSE}
path <- "/u/lestes/spatial_data/globcover_2009/"
if(!file.exists(fp(path, "globSA_alb.tif"))) {
  url <- "http://due.esrin.esa.int/globcover/LandCover2009/Globcover2009_V2.3_Global_.zip"
  download.file(url, method="auto", destfile = "globcover_2009.zip")
  unzip("globcover_2009.zip", exdir= "globcover_2009")
  glob <- raster(fp(path, "GLOBCOVER_L4_200901_200912_V2.3.tif"))
  globSA <- crop(glob, y=sa_buf_gcs)  # crop to extent of SA
  gdalwarp(srcfile = globSA@file@name, 
           dstfile = fp(path, "globSA_alb.tif"), t_srs = prjstr, 
           tr = c(300, 300))
  globSA_alb <- raster(fp(path, "globSA_alb.tif"))
} else {
  globSA_alb <- raster(fp(path, "globSA_alb.tif"))
}

# MODIS landcover 
moddir <- "/u/lestes/spatial_data/MCD12Q1/"
if(!file.exists(fp(moddir, "modis_type_1_alb.tif"))) {
  tiles <- expand.grid("h" = c(19, 20), "v" = c(11, 12))
  tiles <- apply(tiles, 1, function(x) paste("h", x[1], "v", x[2], sep = ""))
  url <- "http://e4ftl01.cr.usgs.gov/MOTA/MCD12Q1.051/2011.01.01/"
  tile.names <- getURL(url, verbose=TRUE, dirlistonly = TRUE) 
  tile.names1 <- strsplit(tile.names, "alt")[[1]]
  tile.names2 <- unique(substr(tile.names1, 20, 64))
  modnames <- tile.names2[sapply(tiles, function(x) grep(x, tile.names2))]
  lapply(modnames, function(x) {
    url <- paste0("http://e4ftl01.cr.usgs.gov/MOTA/MCD12Q1.051/2011.01.01/", x)
    download.file(url, method="auto", destfile = x)
  })
  dir.create("MCD12Q1")
  file.copy(from = dir(pattern = "hdf"), 
            to = paste(getwd(), "MCD12Q1", dir(pattern = "hdf"), sep = "/"))
  file.remove(dir(pattern = "hdf"))

@@

  # Quick convert of one MODIS set to get funny resolution
  setwd(moddir)
  gdal_translate(src_dataset = modis[1], dst_dataset= "modis1.tif", sd_index= 1)
  r <- raster("modis1.tif")
  r <- res(r)

@@

  # warp to albers, mosaic, and clip to SA extent
  lapply(1:5, function(x) {
    print(paste("processing type", x))
    gdalwarp(srcfile = sdnames[[x]], 
             dstfile = paste0("modis_type_", x, "_alb.tif"), 
             t_srs = prjstr, tr = res(r), te = bbox(sa_buf)[1:4])
  })  
  mod_1 <- raster("modis_type_1_alb.tif")
} else {
  mod_1 <- raster(fp(moddir, "modis_type_1_alb.tif"))
}

@@

And then South Africa's landcover database (30 m)
```{r, eval = FALSE}
path <- "/u/lestes/spatial_data/sa_lc_2009/"
setwd("/u/lestes/spatial_data/")
lcnm <- c("sa_ag.tif", "sa_af.tif")
if(length(dir(p_data, pattern = "sa_.*._masked.tif")) != 2) {
  url <- "http://planet.uwc.ac.za/BGISdownloads/landcover_2009.zip"
  download.file(url, method="auto", destfile = "landcover_2009.zip")
  unzip("landcover_2009.zip", exdir = "sa_lc_2009")

@@

  # process masks--extract extract landcover class 2, cultivation, and class 6,
  # plantations, resample, mask with gdal tools
  av <- c(2, 6)
  a <- "sa_lc_2009.tif"
  dang <- Sys.time() 
  salc_l <- lapply(1:2, function(j) {
    print(paste("extracting cover for", lcnm[j]))
    gdal_calc(cstr = paste("A==", av[j], sep = ""), x = list("A" = a), 
              type = "Byte", filename = lcnm[j])
    nm <- fp(p_data, 
                    paste(gsub("\\.tif", "", lcnm[j]), "_masked.tif", sep = ""))
    ext <- sapply(c("xmin", "ymin", "xmax", "ymax"), function(x) {
      slot(extent(sa_r), x)
    })
    print(paste("warping and masking", gsub(p_data, "", nm)))
    gdalwarp(srcfile = lcnm[j], t_srs = projection(sa_r), dstfile = nm, 
             r = "average", ot = "Float32", te = ext, srcnodata = 255, 
             dstnodata = 255, tr = c(1000, 1000), of = "GTiff", verbose = TRUE,
             overwrite = TRUE)
    file.remove(lcnm[j])
    r <- raster(nm)
  })
  Sys.time() - dang

>>>>

Additonal note: This part of the analysis was undertaken on the Linux VM mapper.princeton.edu, using `gdal 1.11`. For full reproducibility of results, this version should be used (`gdalwarp` appears to have different behaviour in older versions when no `-te` (extent) values are passed, which makes the warp slightly different between old and new versions due to different extents after warping).

## Analyses
### Set-up
```{r, eval = FALSE}
library(SAcropland)
library(gdalUtils)
library(RCurl)
# library(RPostgreSQL) # used for initial extraction of sagrid
library(rgdal)
library(rgeos)
library(raster)
```

Paths
```{r, eval = FALSE}
rm(list = ls())
#setwd("/u/lestes/analyses/SAcropland/")
p_root <- proj_root("croplandbias")
p_data <- fp(p_root, "croplandbias/inst/extdata/landcover")
p_dl <- fp(p_root, "croplandbias/external/ext_data/landcover/")

# Note: installed from homebrew gdal 1.11.5, which is older than version with
# QGIS on Sierra (2.1)
getOption("gdalUtils_gdalPath")[[1]]$path

Background data, projections, database connections, and SA grid
```{r, eval = FALSE}
# Get SA shape
data(sashp)
sa_buf <- gBuffer(sashp, width = 3000)

# projections, etc
prjstr <- projection(sashp)
epsg <- data.table(make_EPSG())
gcsstr <- epsg[like(code, "4326"), prj4]

@@

# Connection (deprecated, from old version of mapper.princeton.edu, since 
# updated to have whole Africa grid)
# drv <- dbDriver("PostgreSQL")
# con <- dbConnect(drv, dbname = "SouthAfricaSandbox", user = "postgis", 
#                  password = "P0stG1S")

# Create 1 km grid from sa1kilo to rectify grids against that 
# sql <- paste("SELECT gid, id, ST_AsText(ST_Centroid(geom)) as center", 
#              "FROM sa1kilo")
# geom.tab <- dbGetQuery(con, sql)
# coord.mat <- do.call(rbind, lapply(1:nrow(geom.tab), function(y) {
#   strip <- gsub("POINT|\\(|\\)", "", geom.tab[y, 3])
#   coord.mat <- do.call(rbind, strsplit(strsplit(strip, ",")[[1]], " "))
# }))
# class(coord.mat) <- "numeric"
# point.tab <- cbind(geom.tab[, 1:2], coord.mat)
# colnames(point.tab)[3:4] <- c("x", "y") 
# pointsXYZ <- point.tab[, c(3:4, 2)]
# r <- rasterFromXYZ(pointsXYZ)
# projection(r) <- sa_buf@proj4string
# sa_r <- writeRaster(r, filename = fp(p_data, "sagrid.tif"), 
#                     overwrite = TRUE)
sa_r <- raster(fp(p_data, "sagrid.tif"))

### Bring in landcover datasets
Let's start with the improved/fusion dataset, geo-wiki (note: GLC-Share was also initially tested, but it turned out to be identical to geo-wiki)

```{r, eval = FALSE}
setwd(p_dl)
path <- fp(p_dl, "glc_share")
# url <- "http://www.fao.org/geonetwork/srv/en/resources.get?id=47948&fname=GlcShare_v10_02.zip&acces=private"
url <- paste0("http://www.fao.org/geonetwork/srv/en/resources.get?id=47948&",
              "fname=GlcShare_v10_02.zip&access=private")
download.file(url, method = "auto", destfile = "glc_share.zip")
unzip("glc_share.zip", exdir = "glc_share")
glc <- raster(fp(path, "glc_shv10_02.Tif"))
projection(glc) <- gcsstr
glcSA <- crop(glc, y=sa_buf_gcs, file = fp(path, "glcSA.tif"), 
              overwrite = TRUE)  # crop to SA
gdalwarp(srcfile = glcSA@file@name, 
         dstfile = fp(path, "glcSA_alb.tif"), t_srs = prjstr, 
         tr = c(1000, 1000), r = "bilinear")
glcSA_alb <- raster(fp(path, "glcSA_alb.tif"))

# Warp to SA grid
glcsa <- resample(glcSA_alb, sa_r, method = "bilinear", 
                  filename = fp(path, "glcSA_alb_rect.tif"))
glcsa_m <- mask(glcsa, sa_r, file = fp(p_data, "glcsa_masked.tif"),
                overwrite = TRUE)

```{r, eval = FALSE}
if(!file.exists(fp(p_data, "geowikisa_masked.tif"))) {  # see if file exists, to avoid redoing step 
   # first downloaded manually from password protected geo-wiki site
  # path <- "/u/lestes/spatial_data/geowiki/"
  path <- fp(p_dl, "geowiki/")
  unzip("cropland_hybrid_14052014v8.zip", exdir= "geowiki") 
  # geowiki <- raster(fp(path, "Hybrid_14052014V8.img"))
  geowiki <- raster(fp(path, "Hybrid_14052014V8.img"))
  # projection(geowiki) <- gcsstr
  # crs(geowiki) <- CRS(gcsstr)
  # geowikiSA <- crop(geowiki, y=sa_buf_gcs,
  #                   file = fp(path, "geowikiSA.tif"))  # crop to SA
  geowikiSA <- crop(geowiki, y=sa_buf_gcs, overwrite = TRUE, 
                    file = fp(p_dl, "geowiki/geowikiSA.tif"))  # crop to SA
  gdalwarp(srcfile = filename(geowikiSA), 
           dstfile = fp(path, "geowikiSA_alb.tif"), t_srs = prjstr, 
           tr = c(1000, 1000), r = "bilinear")
  geowikisa_alb <- raster(fp(path, "geowikiSA_alb.tif"))
  geowikisa <- resample(geowikisa_alb, sa_r, method = "bilinear", # Warp to SA
                        filename = fp(path, "geowikisa_alb_rect.tif"))    
  # geowikisa_m <- mask(glcsa, sa_r, 
  geowikisa_m <- mask(geowikisa, sa_r, 
                      file = fp(p_data, "geowikisa_masked.tif"), 
                      overwrite = TRUE)
} else {
  geowikisa_m <- raster(fp(p_data, "geowikisa_masked.tif"))
}

# test
tpath <- "croplandbias/external/ext_data/geowikisa_masked.tif"
geowikisa_mo <- raster(fp(p_root, tpath))
plot(geowikisa_mo - geowikisa_m)

And the standard products, Globcover 2009 and MODIS. Note the URL used originally has been superseded by the one commented out
```{r, eval = FALSE}
path <- "/u/lestes/spatial_data/globcover_2009/"
if(!file.exists(fp(path, "globSA_alb.tif"))) {
  url <- paste0("http://due.esrin.esa.int/globcover/LandCover2009/", 
                "Globcover2009_V2.3_Global_.zip")
  # url <- "http://due.esrin.esa.int/files/Globcover2009_V2.3_Global_.zip"
  download.file(url, method="auto", destfile = "globcover_2009.zip")
  unzip("globcover_2009.zip", exdir= "globcover_2009")
  # glob <- raster(fp(path, "GLOBCOVER_L4_200901_200912_V2.3.tif"))
  glob <- raster(fp(p_dl,
                    "globcover_2009/GLOBCOVER_L4_200901_200912_V2.3.tif"))
  # globSA <- crop(glob, y=sa_buf_gcs)  # crop to extent of SA
  # e <- as(extent(c(-776722.9, 920077.1, -3831848, -2385248)),
  #                "SpatialPolygons")
  # crs(e) <- CRS(prjstr)
  # e <- spTransform(e, CRS(gcsstr))
  # globSA <- crop(glob, y = e, overwrite = TRUE,
  globSA <- crop(glob, y = sa_buf_gcs, overwrite = TRUE,
                 filename = fp(p_dl, "globcover_2009/globSA.tif"))  # crop
  # gdalwarp(srcfile = filename(globSA), overwrite = TRUE, 
  gdalwarp(srcfile = filename(globSA), overwrite = TRUE, 
           dstfile = fp(p_dl, "globSA_alb.tif"), t_srs = prjstr,
           # tap = TRUE,
           # dstfile = fp(path, "globSA_alb.tif"), t_srs = prjstr, 
           tr = c(300, 300))#, te = extent(e)[1:4])
  # globSA_alb <- raster(fp(path, "globSA_alb.tif"))
  globSA_alb <- raster(fp(p_dl, "globSA_alb.tif"))
} else {
  globSA_alb <- raster(fp(path, "globSA_alb.tif"))
}

# MODIS landcover 
# moddir <- "/u/lestes/spatial_data/MCD12Q1/"
moddir <- fp(p_dl, "MCD12Q1")
if(!file.exists(fp(moddir, "modis_type_1_alb.tif"))) {
  tiles <- expand.grid("h" = c(19, 20), "v" = c(11, 12))
  tiles <- apply(tiles, 1, function(x) paste("h", x[1], "v", x[2], sep = ""))
  url <- "http://e4ftl01.cr.usgs.gov/MOTA/MCD12Q1.051/2011.01.01/"
  tile.names <- getURL(url, verbose=TRUE, dirlistonly = TRUE) 
  tile.names1 <- strsplit(tile.names, "alt")[[1]]
  tile.names2 <- unique(substr(tile.names1, 20, 64))
  modnames <- tile.names2[sapply(tiles, function(x) grep(x, tile.names2))]
  lapply(modnames, function(x) {
    url <- paste0("http://e4ftl01.cr.usgs.gov/MOTA/MCD12Q1.051/2011.01.01/", x)
    download.file(url, method="auto", destfile = x)
  })
  dir.create("MCD12Q1")
  file.copy(from = dir(pattern = "hdf"), 
            to = paste(getwd(), "MCD12Q1", dir(pattern = "hdf"), sep = "/"))
  file.remove(dir(pattern = "hdf"))

@@

  # Quick convert of one MODIS set to get funny resolution
  setwd(moddir)
  gdal_translate(src_dataset = modis[1], dst_dataset= "modis1.tif", 
                 sd_index= 1)
  r <- raster("modis1.tif")

@@

  # warp to albers, mosaic, and clip to SA extent
  lapply(1:5, function(x) {
    print(paste("processing type", x))
    gdalwarp(srcfile = sdnames[[x]], 
             dstfile = paste0("modis_type_", x, "_alb.tif"), 
             t_srs = prjstr, tr = res(r), te = bbox(sa_buf)[1:4])
  })  
  mod_1 <- raster("modis_type_1_alb.tif")
  file.remove(dir(moddir, pattern = "MCD12Q1"))
} else {
  mod_1 <- raster(fp(moddir, "modis_type_1_alb.tif"))
}

@@

And then South Africa's landcover database (30 m)
```{r, eval = FALSE}
# path <- "/u/lestes/spatial_data/sa_lc_2009/"
# setwd("/u/lestes/spatial_data/")
path <- fp(p_dl, "sa_lc_2009/")
lcnm <- c("sa_ag.tif", "sa_af.tif")
if(length(dir(p_data, pattern = "sa_.*._masked.tif")) != 2) {
  url <- "http://planet.uwc.ac.za/BGISdownloads/landcover_2009.zip"
  download.file(url, method="auto", destfile = "landcover_2009.zip")
  unzip("landcover_2009.zip", exdir = "sa_lc_2009")

@@

  # process masks--extract extract landcover class 2, cultivation, and class 6,
  # plantations, resample, mask with gdal tools
  av <- c(2, 6)
  a <- "sa_lc_2009.tif"
  dang <- Sys.time() 
  salc_l <- lapply(1:2, function(j) {
    print(paste("extracting cover for", lcnm[j]))
    gdal_calc(cstr = paste("A==", av[j], sep = ""), x = list("A" = a), 
              type = "Byte", filename = lcnm[j])
    # nm <- fp(p_data, paste0(gsub("\\.tif", "", lcnm[j]), "_masked.tif"))
    nm <- fp(path, paste0(gsub("\\.tif", "", lcnm[j]), "_masked.tif"))
    ext <- sapply(c("xmin", "ymin", "xmax", "ymax"), function(x) {
      slot(extent(sa_r), x)
    })
    print(paste("warping and masking", gsub(path, "", nm)))
    gdalwarp(srcfile = lcnm[j], t_srs = projection(sa_r), dstfile = nm, 
             r = "average", ot = "Float32", te = ext, srcnodata = 255, 
             dstnodata = 255, tr = c(1000, 1000), of = "GTiff", verbose = TRUE,
             overwrite = TRUE)
    file.remove(lcnm[j])
    r <- raster(nm)
  })
  Sys.time() - dang

### 2017-08-31 Rmd/c9-agent-based-model.Rmd
Gigantic first commit of croplandbias repo after being cloned and renamed from SAcropland. Significant changes: 1. Rerrangement of data structure structure--key intermediate inputs/outputs will be kept in inst/extdata/subfolder to install as R library; some other smaller ones are in data/ 2. Paper and figures are in inst/paper 3. Code has been re-run from c1-c9 (yield-production). Numbering of code chapters has been changed because landcover dataset download steps were placed first in standalone chapter (c1-landcover-fetch) 4. Analysis chapters are now stored as vignettes. Rmd folder is staged

---
title: "Bias in Allocation of ABM Agents"
author: "Lyndon Estes"
date: "June 26, 2015"
output: 
  html_document:
    highlight: tango
    theme: spacelab
    toc: yes 
    number_sections: true
---

# Overview

@@

# Data
```{r, eval=FALSE}
library(SAcropland)
library(raster)
library(rgdal)
library(lmisc)
library(readxl)
library(rgeos)

@@

## Magisterial District selection

@@

### Map selected districts, cropland percentage, and bias
```{r, eval = FALSE}
brks1 <- seq(0, 100, 10)
cols1 <- rev(terrain.colors(length(brks1) - 1))
brks2 <- c(-100, -80, -60, -40, -20, -10, -5, -1)
brks2 <- c(brks2, rev(abs(brks2)))
cols2 <- colorRampPalette(c("red", "grey80", "blue4"))(length(brks2) - 1)
cols2[c(1, length(cols2))] <- c("darkred", "purple3")
cx <- 1.1
lcol <- "black"
mcap <- c("SA-LC", "GlobCover", "MODIS", "GeoWiki")

@@

# Select modeled yields for agent-based model

@@

# Downscaling and agent allocation

Performed separately and described in the methods.

# Analysis of agent allocation bias
```{r, eval = FALSE}
abias <- data.table(read_excel(full_path(p_data, "abm/stats.xlsx")))
# abias <- abias[Alg == 1]
setkey(abias, MD)
hhs <- data.table(read_excel(full_path(p_data, "abm/agent-bias2.xlsx"), 
                             sheet = 2))
setkey(hhs, MD)
abias <- abias[hhs]
abias

>>>>

---
title: "Agent-based model sensitivity"
author: "Lyndon Estes"
date: "June 26, 2015"
output: 
  html_document:
    highlight: tango
    theme: spacelab
    toc: yes 
    number_sections: true
---

# Agent-based model sensitivity to map error

@@

## Data
```{r, eval=FALSE}
library(SAcropland)
library(raster)
library(rgdal)
library(lmisc)
library(readxl)
library(rgeos)

@@

### Magisterial District selection

@@

### Map selected districts, cropland percentage, and error
```{r, eval = FALSE}
brks1 <- seq(0, 100, 10)
cols1 <- rev(terrain.colors(length(brks1) - 1))
brks2 <- c(-100, -80, -60, -40, -20, -10, -5, -1)
brks2 <- c(brks2, rev(abs(brks2)))
cols2 <- colorRampPalette(c("red", "grey80", "blue4"))(length(brks2) - 1)
cols2[c(1, length(cols2))] <- c("darkred", "purple3")
cx <- 1.1
lcol <- "black"
mcap <- c("SA-LC", "GlobCover", "MODIS", "GeoWiki")

@@

## Select modeled yields for agent-based model

@@

## Downscaling and agent allocation

Performed separately and described in the methods and supplemental.

## Analysis of agent allocation errors
```{r, eval = FALSE}
abias <- data.table(read_excel(full_path(p_data, "abm/stats.xlsx")))
# abias <- abias[Alg == 1]
setkey(abias, MD)
hhs <- data.table(read_excel(full_path(p_data, "abm/agent-bias2.xlsx"), 
                             sheet = 2))
setkey(hhs, MD)
abias <- abias[hhs]
abias

### 2017-08-31 Rmd/c99-misc.Rmd
Commit multiple changes to Appendix, including restructuring and renaming of Rmd files to faciliate creation of single code appendix, removal of many files from repo and into gitignore. Significance statement added to main ms.
Gigantic first commit of croplandbias repo after being cloned and renamed from SAcropland. Significant changes: 1. Rerrangement of data structure structure--key intermediate inputs/outputs will be kept in inst/extdata/subfolder to install as R library; some other smaller ones are in data/ 2. Paper and figures are in inst/paper 3. Code has been re-run from c1-c9 (yield-pr

---
title: "Miscallaneous calculations"
author: "Lyndon Estes"
date: "August 24, 2015"
output: 
  html_document:
    highlight: tango
    theme: spacelab
    toc: yes 
    number_sections: true
---

Various small calculations made for the analysis.

```{r, eval=FALSE}
library(rgdal)
library(SAcropland)
library(rgeos)

>>>>

---
title: "Miscellaneous calculations"
author: "Lyndon Estes"
date: "August 24, 2015"
output: 
  html_document:
    highlight: tango
    theme: spacelab
    toc: yes 
    number_sections: true
---

# Miscellaneous additional calculations

```{r, message=FALSE}
library(rgdal)
library(SAcropland)
library(rgeos)
library(lmisc)

### 2017-08-31 Rmd/compile-book.Rmd
Gigantic first commit of croplandbias repo after being cloned and renamed from SAcropland. Significant changes: 1. Rerrangement of data structure structure--key intermediate inputs/outputs will be kept in inst/extdata/subfolder to install as R library; some other smaller ones are in data/ 2. Paper and figures are in inst/paper 3. Code has been re-run from c1-c9 (yield-production). Numbering of code chapters has been changed because landcover dataset download steps were placed first in standalone chapter (c1-landcover-fetch) 4. Analysis chapters are now stored as vignettes. Rmd folder is staged

Solution from [here](http://stackoverflow.com/questions/25824795/how-to-combine-two-rmarkdown-rmd-files-into-a-single-output).
```{r, eval=FALSE}
d <- "Rmd"
a <- "---\ntitle: 'Code Appendix'\noutput:\n  pdf_document:\n    toc: yes\n"
b <- "    toc_depth: 4\n    highlight: tango\n    number_sections: yes\n---"
book_header <- readLines(textConnection(paste0(a, b)))
# book_header <- readLines(textConnection("---\ntitle: 'Title'\n---"))
old <- setwd(d)
if(length(grep("code.Rmd", list.files())) > 0){
  warning("code.Rmd already exists")
}
write(book_header, file = "code.Rmd", )
cfiles <- list.files(pattern = "[0-9].*.Rmd")
ttext <- NULL
for(i in 1:length(cfiles)){
  text <- readLines(cfiles[i])
  hspan <- grep("---", text)
  text <- text[-c(hspan[1]:hspan[2])]
  write(text, sep = "\n", file = "code.Rmd", append = TRUE)
}
```

>>>>

Solution from [here](http://stackoverflow.com/questions/25824795/how-to-combine-two-rmarkdown-rmd-files-into-a-single-output).
```{r, eval=FALSE}
d <- "Rmd"
a <- "---\ntitle: 'Code Appendix'\noutput:\n  pdf_document:\n    toc: yes\n"
b <- "    toc_depth: 4\n    highlight: tango\n    number_sections: yes\n---"
book_header <- readLines(textConnection(paste0(a, b)))
# book_header <- readLines(textConnection("---\ntitle: 'Title'\n---"))
old <- setwd(d)
if(length(grep("code.Rmd", list.files())) > 0){
  warning("code.Rmd already exists")
}
write(book_header, file = "code.Rmd", )
cfiles <- list.files(pattern = "[0-9].*.Rmd")
reord <- order(as.numeric(gsub("c|-.*", "", cfiles)))
cfiles <- cfiles[(1:length(cfiles))[reord]]
ttext <- NULL
for(i in 1:length(cfiles)){
  text <- readLines(cfiles[i])
  hspan <- grep("---", text)
  text <- text[-c(hspan[1]:hspan[2])]
  write(text, sep = "\n", file = "code.Rmd", append = TRUE)
}
```

### 2017-08-31 inst/paper/figures/totC-bias.tex
Gigantic first commit of croplandbias repo after being cloned and renamed from SAcropland. Significant changes: 1. Rerrangement of data structure structure--key intermediate inputs/outputs will be kept in inst/extdata/subfolder to install as R library; some other smaller ones are in data/ 2. Paper and figures are in inst/paper 3. Code has been re-run from c1-c9 (yield-production). Numbering of code chapters has been changed because landcover dataset download steps were placed first in standalone chapter (c1-landcover-fetch) 4. Analysis chapters are now stored as vignettes. Rmd folder is staged

% latex table generated in R 3.2.1 by xtable 1.7-4 package
% Sun Nov  1 15:16:19 2015
\begin{table}[ht]
\centering
\caption{Percent differences in total carbon stock estimates calculated from the reference maps and from each of the four cropland maps. Differences are evaluated for total carbon estimates either at the country scale or over just the agricultural regions (cropland $>$0.05\%), using the carbon densities of 5 different cover types to provide the values for the non-agricultural portions of each pixel (cover types indicated by column names).} 
\begin{tabular}{llrrrrr}
  \hline
Region & Map & Forest & Secondary & Shrubland & Grassland & Sparse \\ 
  \hline
Country & SA-LC & 2.6 & 2.5 & 2.5 & 0.1 & -2.1 \\ 
  Country & GlobCover & -2.1 & -2.0 & -2.0 & -0.1 & 1.7 \\ 
  Country & MODIS & -2.6 & -2.5 & -2.5 & -0.1 & 2.1 \\ 
  Country & GeoWiki & 0.6 & 0.5 & 0.5 & 0.0 & -0.5 \\ 
  Agricultural & SA-LC & -2.0 & -2.7 & -2.8 & -10.6 & -14.9 \\ 
  Agricultural & GlobCover & -161.9 & -156.3 & -155.5 & -95.9 & -63.6 \\ 
  Agricultural & MODIS & -1.6 & -0.8 & -0.7 & 8.4 & 13.3 \\ 
  Agricultural & GeoWiki & 7.7 & 7.3 & 7.2 & 2.9 & 0.5 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

% latex table generated in R 3.4.1 by xtable 1.8-2 package
% Mon Aug 28 06:26:20 2017
\begin{table}[ht]
\centering
\caption{Percent differences in total carbon stock estimates calculated from the reference maps and from each of the four cropland maps. Differences are evaluated for total carbon estimates either at the country scale or over just the agricultural regions (cropland $>$0.05\%), using the carbon densities of 5 different cover types to provide the values for the non-agricultural portions of each pixel (cover types indicated by column names).} 
\begin{tabular}{llrrrrr}
  \hline
Region & Map & Forest & Secondary & Shrubland & Grassland & Sparse \\ 
  \hline
Country & SA-LC & 2.6 & 2.5 & 2.5 & 0.1 & -2.1 \\ 
  Country & GlobCover & -2.1 & -2.0 & -2.0 & -0.1 & 1.7 \\ 
  Country & MODIS & -2.6 & -2.5 & -2.5 & -0.1 & 2.1 \\ 
  Country & GLC-Share & 0.6 & 0.5 & 0.5 & 0.0 & -0.5 \\ 
  Agricultural & SA-LC & -2.0 & -2.7 & -2.8 & -10.6 & -14.9 \\ 
  Agricultural & GlobCover & -161.9 & -156.3 & -155.5 & -95.9 & -63.6 \\ 
  Agricultural & MODIS & -1.6 & -0.8 & -0.7 & 8.4 & 13.3 \\ 
  Agricultural & GLC-Share & 7.7 & 7.3 & 7.2 & 2.9 & 0.5 \\ 
   \hline
\end{tabular}
\end{table}
